\textbf{Designing a Security Management Layer with Copy-on-Write for CDN Assets}

### 2016-03-21 tex/paper.tex
Rewrote eventual consistency

%}}}
\begin{abstract}
This work presents a technique for incorporating Copy-on-Write in a high level system on top of an
unaware persistent storage. The system in this case is a security management system, but the
technique and conclusions drawn are general enough to be applicable to any system with vaguely
similar consistency requirements. The scalability of the system is tested and the technique is
evaluated. The technique is shown to be quite efficient (scalable to >6000 simultaneous active
users per node), but a better solution is also suggested in the conclusion.\\

@@

\subsubsubsection{GUID}
Global Unique Identifier - Usually in distributed environments normal incremented identifiers can
not be used as there can be insertions on several nodes at the same time. A GUID is generated by a
function that makes it impossible or extremely unlikely that the same identifier will be generated
and used again.

\subsubsubsection{JPF}
Java Path Finder - It was developed by NASA and in 2005 they released it under an open source
license, which made more people contribute to the project. JPF is usually used for doing model
checking of concurrent programs to easily find for example race conditions and deadlocks.

\subsubsection{Terms}
\subsubsubsection{Eventual Consistency}
The expression eventual consistency is a term used for describing how data is processed. It is often
used in the context of database systems. Eventual consistency means that stored data is guaranteed 
to be consistent in any one moment, but at some point the data will eventually converge to being 
consistent~\cite{EVENTUAL}.

The effect of this is that persistent storages, especially distributed databases, can
operate faster as there is no need for locks and transactions for any operations. As no locks or
transactions are used, operations on the same entities can be done before earlier operations have
propagated to all nodes. This can mean that the system ends up in a state where there is a conflict
that needs to be handled, for example two operations that wants to change the same data at once. To
solve this the system needs to have defined which operation that will take precedence, or how the
concurrent operations are mixed, and this is usually called conflict or sibling resolution.

@@

\subsection{Data integrity}
A computer system or subsystem is defined as possessing the property of integrity if it behaves consistently
according to a defined standard. This implies that a subsystem possessing the property of integrity
does not guarantee an absolute behaviour of the system, but rather that it performs according to
what its creator intended ~\cite{BIBA}.
\\
The invariant for this model is the file. Which means that it shouldn't be possible to
change a file though out the cycle of operation without creating a new file object with a new
identifier. This is to ensure that files can not lose their integrity by simultaneous
operations from different nodes or get mixed up when referred to from a content object.

>>>>

%}}}
\begin{abstract}
This work presents a technique for incorporating Copy-on-Write on top of an unaware persistent
storage. The system in this case is a security management system, but the technique and conclusions
drawn are general enough to be applicable to any system with vaguely similar consistency
requirements. The scalability of the storage system is tested and the technique is evaluated. The
technique is shown to be quite efficient (scalable to >6.000 simultaneous active users per node),
but a better solution is also suggested in the conclusion.\\

@@

\subsubsubsection{GUID}
Global Unique Identifier - In distributed environments normal incremented identifiers can
not be used as there can be insertions on several nodes at the same time. A GUID is generated by a
function that makes it impossible or extremely unlikely that the same identifier will be generated
and used again.

\subsubsubsection{JPF}
Java Path Finder was developed by NASA and in 2005 they released it under an open source
license, which made more people contribute to the project. JPF is usually used for doing model
checking of concurrent programs to easily find for example race conditions and deadlocks.

\subsubsection{Terms}
\subsubsubsection{Eventual Consistency}
Eventual consistency is an informal guarantee that defines how the consistency of stored data can
behave. In a system defined as using eventual consistency, access to stored data is not guaranteed
to return the result of the latest modification. At some point, if modifications to the stored data
stop, access to a data item will return the resulting data of the last modification of that
item.~\cite{EVENTUAL}. It is often used in the context of database systems.

The effect of the lack of a strong consistency requirement is that persistent storages, especially
distributed databases, can operate faster since there is no need for locks or transactions.  This
results in that operations on the same items can be made before earlier operations have propagated
to all the distributed nodes.

A system using eventual consistency can end up in a state where there is a conflict that needs to be
handled. If for example two concurrent operations performed on two different servers changes the
same data item, a conflict of how the resulting item should look like will occur when synchronising
these servers. To solve the conflict the system needs to have a defined set of rules to be able to
determine which operation that will take precedence, or how the concurrent operations are mixed, and
this is usually called conflict or sibling resolution.

@@

\subsection{Data integrity}
A computer system or subsystem is defined as possessing the property of integrity if it behaves consistently
according to a defined standard. This implies that a subsystem possessing the property of integrity
does not guarantee an absolute behaviour of the system, but rather that it performs according to
what its creator intended ~\cite{BIBA}.
\\
The invariant for this model is the file. Which means that it should not be possible to
change a file though out the cycle of operation without creating a new file object with a new
identifier. This is to ensure that files can not lose their integrity by simultaneous
operations from different nodes or get mixed up when referred to from a content object.
